### 2013-01-13 report/paper_mathsaey.tex
Added code examples and the section about constructors

\documentclass[12pt, a4paper, twocolumn]{article}

@@

@@

%Title + table of contents
\input{content/titlepage}
\tableofcontents
\newpage
%Content

@@

It's also worth mentioning that Objective-C does allow you to access a protected variable outside of the class. The compiler generates a warning, but still allows you to do this. The following warning is shown: 
\textit{"warning: instance variable ‘b’ is @protected; this will be a hard error in the future"}.
Furthermore, the reflective features of Objective-C still allow a programmer to access private instance variables. This is because access modifiers are checked at compile time and not at runtime. Reflection is mentioned in greater detail in section \ref{sec:reflect}

@@

@@

\section{Appendix}
\input{content/listings}

>>>>

\documentclass[11pt, a4paper, twocolumn]{article}

@@

\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

@@

%Title + table of contents
\input{content/titlepage}
\tableofcontents
%Content

@@

It's also worth mentioning that Objective-C does allow you to access a protected variable outside of the class. The compiler generates a warning, but still allows you to do this. The following warning is shown: 
\textit{"warning: instance variable ‘b’ is @protected; this will be a hard error in the future"}.
Furthermore, the reflective features of Objective-C still allow a programmer to access private instance variables. This is because access modifiers are checked at compile time and not at runtime. Reflection is mentioned in greater detail in section \ref{sec:reflection}

@@

\subsection{Constructors and Destructors}
\label{sec:constructor}
C++ constructors are normal methods with no return type and the class name as their signature. Method overloading (see section \ref{sec:overloading}) allows the definition of multiple constructors. Destructors in C++ are declared in a similar way, however, a destructor cannot accept any arguments and is named "\textit{\mytilde{}Classname()}". A destructor will be automatically called right before deleting an object.

The Objective-C language has no mandatory constructors or destructors. Constructing and deconstructing an object generally happens by overriding a few methods inherited from NSObject. These methods are listed here: 
\begin{itemize}
\item \textbf {alloc} Alloc allocates the space that the object needs.
\item \textbf {init} Init inialises the necessary instance variables.
\item \textbf {dealloc} Dealloc releases all the instance variables.
\end{itemize}

Note that nothing prevents an Objective-C programmer from creating his own alloc, init or dealloc that don't derive from NSObject directly or indirectly. For instance, a programmer that wants to implement the singleton pattern generally overrides alloc to ensure that an object is only created when he wants it.
Initialisers generally derive from NSObject's init at some point (via a call to super init). Conventions dictate that initialisers start with init. Multiple initialisers are simply constructed by creating different methods, note that an initisialiser should return itself after instantiating the necessary instance variables.

\section{Lanaguage-Specific \\ Features}
\subsection{Objective-C}
\subsubsection{Protocols}
\label{sec:protocol}

\subsubsection{Categories}
\label{sec:categories}

\subsubsection{Message Forwarding}
\label{sec:message}

\subsubsection{Reflection}
\label{sec:reflection}

\subsubsection{Metaclasses}
\label{sec:meta}

\subsection{C++}
\subsubsection{Method Overloading}
\label{sec:overloading}

\subsubsection{Namespaces}
\label{sec:namespaces}

\subsubsection{Abstract Classes}
\label{sec:abstract}

\subsubsection{Friend Classes}
\label{sec:friend}

\subsubsection{Inner Classes}
\label{sec:inner}

\section{Conclusion}

@@

\section{Code Listings}
\input{content/listings}
